---
output: html_document
---

```{r setup code, warning=FALSE, include=FALSE}
library(raster)
library(tidyverse)
library(sf)
library(scales)
library(ggspatial)
library(viridis)
library(knitr)
library(isotone)

options(scipen = 999)

## load datasets
load("local_data/census.RData")
load("service_areas.RData")
load("stations.RData")
load("vehicles.RData")
load("muds.RData")
load("commute_chargers.RData")

colorscheme <- "viridis"

## set property name
property_name <- "Oakland - Lake Park"
maplabel  <- "Oakland - Lake Park"

## extract city from address
city <- 
  hpcp_list_geocode %>%
  filter(property == property_name) %>%
  pull(address) %>% 
  str_extract("(?<=, ).+,.+(?=, \\d{5}$)")

## evse charachteristics 
power <-
  hpcp_list_geocode %>% 
  filter(property == property_name) %>% 
  pull(charger_kw)

chargers <-
  hpcp_list_geocode %>% 
  filter(property == property_name) %>% 
  pull(num_chargers) %>% 
  str_replace("3", "three") %>% 
  str_replace("4", "four") %>% 
  str_replace("6", "six")

# horizontal bar graph theme
theme_evgo_hbar <- function() {
  theme_minimal() %+replace%
    theme(
      axis.line.x = element_line(size = 0.05, color = "#a3a3a3"),
      panel.grid.major.x = element_line(size = 0.05, color = "#ebebeb"),
      panel.grid.minor.x = element_line(size = 0.05, color = "#ebebeb"),
      panel.grid.major.y = element_blank(),
      axis.text.y = element_text(size = 9, color = "#525252", hjust = 1),
      axis.text.x = element_text(size = 10, color = "#525252"),
      axis.title = element_text(size = 13, color = "#525252", hjust = -0.008, face = "bold"),
      legend.position = "bottom",
      legend.box.spacing = unit(-.4, "cm"),
      legend.title = element_text(size = 9, color = "#525252", vjust = 0.7),
      legend.text = element_text(size = 8, color = "#525252", vjust = 0.7),
      plot.margin = unit(c(0, 0, 0, 0), units = "cm")
    )
}

theme_evgo_vbar <- function() {
  theme_minimal() %+replace%
    theme(
      axis.line.x = element_line(size = 0.05, color = "#a3a3a3"),
      panel.grid.major.y = element_line(size = 0.05, color = "#ebebeb"),
      panel.grid.minor.y = element_line(size = 0.05, color = "#ebebeb"),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      axis.text.y = element_text(size = 13, color = "#525252", hjust = 1),
      axis.text.x = element_text(size = 10, color = "#525252"),
      axis.title = element_text(size = 13, color = "#525252", hjust = -0.008, face = "bold"),
      legend.position = "bottom",
      legend.box.spacing = unit(-.4, "cm"),
      plot.margin = unit(c(0, 0, 0, 0), units = "cm")
      
    )
}

# map graphic theme
theme_evgo_map <- function() {
  theme_minimal() %+replace%
    theme(
      axis.line.x = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      axis.text.y = element_blank(),
      axis.text.x = element_blank(),
      axis.title = element_blank(),
      legend.position = "bottom",
      plot.margin = unit(c(0, 0, 0, 0), units = "cm"),
      legend.box.margin=margin(-3,-3,-3,-3)
    )
}


## histogram theme
theme_evgo_hist <- function() {
  theme_minimal() %+replace%
    theme(
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.y = element_line(size = .25, color = "#ebebeb"),
      panel.grid.minor.y = element_line(size = .25, color = "#ebebeb"),
      axis.text.y = element_text(size = 10, color = "#525252"),
      axis.text.x = element_text(size = 10, color = "#525252"),
      axis.title.x = element_text(size = 13, color = "#525252", hjust = 0, face = "bold"),
      legend.position = "bottom",
      legend.box.spacing = unit(-.4, "cm"),
      plot.margin = unit(c(0, 0, 0, 0), units = "cm")
      
    )
}
```
# `r property_name` - baseline factsheet
The *`r property_name`* High Power Charging Plaza is located in `r city`. The station has 
`r chargers` `r power`kW chargers  

```{r define map aspect ratio, echo=FALSE}
boundingbox <- 
local_service_area %>%
  filter(property == property_name) %>% 
  arrange(contour) %>% 
  mutate(travel_time = paste(contour,"min") %>% 
                       fct_reorder(contour) %>% 
                       fct_rev()) %>%
  
  st_transform(4326) %>% 
  
  st_bbox()

width <- (boundingbox$xmax - boundingbox$xmin) %>% unname()
length <-(boundingbox$ymax - boundingbox$ymin) %>% unname()

if (length > width) {
  width_add <-  (length - width)/2
  
  xlimits <- c(unname(boundingbox$xmin) - (width_add),
               unname(boundingbox$xmax) + (width_add))
  ylimits <- c(unname(boundingbox$ymin), unname(boundingbox$ymax))
  
  
  
} else {
  length_add <- (width - length)/2
  
  ylimits <- c(unname(boundingbox$ymin) - (length_add),
               unname(boundingbox$ymax) + (length_add))
  xlimits <- c(unname(boundingbox$xmin), unname(boundingbox$xmax))
  
}

```



```{r service area map, echo=FALSE, fig.height=7.5, fig.width=5.5, dpi=300}

# filter
local_service_area %>%
  filter(property == property_name) %>% 
  arrange(contour) %>% 
  mutate(travel_time = paste(contour,"min") %>% 
                       fct_reorder(contour) %>% 
                       fct_rev()) %>%
  
  st_transform(4326) %>%  

# plot map    
ggplot() +
  
  theme_evgo_map() +
  
  
  annotation_map_tile(type = "cartolight", zoom = 14, progress = c("none")) +

  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  geom_sf(aes(fill = travel_time),
          alpha = 0.6,
          color = "white") +
  xlab(NULL)+
  ylab(NULL)+
  
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +

  coord_sf(xlim = xlimits, ylim = ylimits) +
  
  geom_curve(data = hpcp_list_geocode %>% 
                    filter(property == property_name) %>% 
                    mutate(st_lon = lon + 0.015,
                           st_lat = lat - 0.015),
             
             aes(x = st_lon, y = st_lat, xend = lon, yend = lat),
             color = "#383838",
             curvature = -0.2,
             arrow = arrow(length = unit(0.2, "cm"), type = "closed"),
             size = 0.2,
             lineend = "round"
  ) +

 annotate(geom = "text",
          x = hpcp_list_geocode %>% 
            filter(property == property_name) %>% 
            pull(lon) + 0.015,
          y = hpcp_list_geocode %>% 
            filter(property == property_name) %>% 
            pull(lat) - 0.015,
          label = maplabel,
          hjust = 0,
          color = "#383838",
          size = 3.5
)



```

### Neighborhood service area  
The neighborhood service area represents HCPC accessibility to residents of nearby MuDs.
The area is defined by travel time. Service areas are broken down into three polygons (isochrones)
defined by the distance a vehicle can travel in 5, 7, and 10 minutes in freeflowing traffic.  

The relationship between travel time and the area is non-linear (e.g a 2x increase in travel time = >2x
increase in area) As travel time increases, the number of MuDs encompassed by the service area grows, and 
relative demographic indicators such as race/ethnicity or income may change. At the same time, the availability 
of alternative charging options also grows.  

**Fast Charge capable EVs**  
*registered vehicles*  
```{r echo=FALSE, fig.height = 2, fig.width = 5.5, dpi = 300}
library(scales)

max_value <- dc_fast_bev  %>% 
  filter(property == property_name) %>%
  pull(bev_num) %>%
  max()
  
dc_fast_bev %>% 
  filter(property == property_name) %>%
  arrange(desc(contour)) %>% 
  mutate(travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev()
  ) %>% 

ggplot(aes(x = tesla, fill = travel_time)) +
  
  theme_evgo_hbar() +
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  geom_col(aes(y = bev_num), 
           position = position_dodge(width = .8),
           width = 0.7) +
  
  geom_text(aes(y = bev_num, label = comma(bev_num)),
           position = position_dodge(width = .8),
           hjust = -0.2) +
  
  scale_y_continuous(name = "", 
                     expand = expand_scale(mult = c(0, .01)),
                     limits = c(0, max_value * 1.08),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)) +
  
  xlab("") +
  coord_flip()
```
\
**DC Fast Chargers**   
*inside or within 1 mile of service area*  
```{r echo=FALSE, fig.height=2, fig.width=5.5, dpi = 300}

library(scales)

dcfc_complete <- dcfc_summary %>% 
  complete(property, nesting(contour, charge_network), fill = list(dcfc = 0)) %>% 
  filter(property == property_name) %>%
  group_by(charge_network) %>% 
  mutate(group_test = sum(dcfc)) %>% 
  ungroup() %>% 
  filter(group_test != 0) %>% 
  dplyr::select(-group_test) %>% 
  arrange(desc(contour)) %>% 
  mutate(travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev()
  ) 

max_value <- 
  dcfc_complete %>% 
  pull(dcfc) %>% 
  max()

dcfc_complete %>% 
ggplot(aes(x = charge_network, fill = travel_time)) +
  
  theme_evgo_hbar() +
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  geom_col(aes(y = dcfc), 
           position = position_dodge(width = .8),
           width = 0.75) +
  
  geom_text(aes(y = dcfc, label = comma(dcfc)),
           position = position_dodge(width = 0.8),
           hjust = - 0.2) +
  
  scale_y_continuous(name = "", 
                     expand = expand_scale(mult = c(0, .01)),
                     limits = c(0, max_value * 1.08),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)) +
  xlab("")+
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE))

```
\
**Public l2 chargers**   
*inside and within 1/2 mile of service area boundary*  
```{r echo=FALSE, fig.height=1, fig.width=5.5, dpi = 300}

library(scales)

l2_graph <- l2_summary %>% 
  filter(property == property_name) %>%   
  mutate(travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev())

max_value <- l2_graph %>% 
  pull(l2_chargers) %>% 
  max()

ggplot(l2_graph) +
  
  theme_evgo_hbar() +
  
  theme(
    legend.position = "none",
  ) +
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  geom_col(aes(x = travel_time, y = l2_chargers, fill = travel_time), 
           position = "identity",
           width = 0.8) +
  
  geom_text(aes(x = travel_time, y = l2_chargers, label = comma(l2_chargers)), 
           position = "identity",
           hjust = -0.2) +
  
  scale_y_continuous(name = "",
                     labels = comma,
                     expand = expand_scale(mult = c(0, 0)),
                     limits = c(0, max_value * 1.08),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)) +
  xlab("") +

  
  coord_flip()

```
\
**Number of multi-unit dwelling units**  
*by units in building*  
```{r echo=FALSE, fig.height=4, fig.width=5.5, dpi = 300}
max_value <- units_buildings  %>% 
  filter(property == property_name) %>%
  pull(estimate) %>%
  max()
  
units_buildings %>% 
  filter(property == property_name) %>%
  arrange(desc(contour)) %>% 
  mutate(
    var_name_order = str_extract(var_name, "^\\d+") %>% as.numeric(),
    var_name = fct_reorder(var_name, var_name_order) %>% fct_rev(),
    travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev()
  ) %>% 

ggplot(aes(x = var_name, y = estimate, fill = travel_time)) +
  
  theme_evgo_hbar() +
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  geom_col(position = position_dodge(width = .8),
           width = 0.7) +
  
  geom_text(aes(label = comma(estimate)),
           position = position_dodge(width = .8),
           hjust = -0.1,
           vjust = .4) +
  
  scale_y_continuous(name = "",
                     labels = comma,
                     expand = expand_scale(mult = c(0, .01)),
                     limits = c(0, max_value * 1.13),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)) +
  
  guides(fill = guide_legend(reverse = TRUE)) +
  
  xlab("") +
  coord_flip()


```

\
**Share of renters and homeowners**  
```{r echo=FALSE, fig.height=2, fig.width=5.5, dpi=300}

max_value <- renter_share  %>% 
  filter(property == property_name) %>%
  pull(percentage) %>%
  max()

renter_share %>% 
  filter(property == property_name) %>%
  arrange(desc(contour)) %>% 
  mutate(
         travel_time = fct_reorder(paste(contour, "min"), contour) %>%  fct_rev()
  ) %>% 
  
  #plot
  ggplot(aes(x = var_name, y = percentage, fill = travel_time)) +
  
    
  theme_evgo_hbar() +
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
    geom_col(position = position_dodge(width = .8),
           width = 0.7) +
  
    geom_text(aes(label = percent(percentage)),
           position = position_dodge(width = .8),
           hjust = -0.1,
           vjust = .4) +
  
  scale_y_continuous(name = "",
                     labels = percent,
                     expand = expand_scale(mult = c(0, 0)),
                     limits = c(0, max_value * 1.15),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)) +

  xlab("") +
  
  guides(fill = guide_legend(reverse = TRUE)) +
  
  coord_flip()

```
\
### Income and demographics

**Neighborhood service area population by travel time:**  
```{r echo=FALSE, fig.height=1, fig.width=5.5, dpi = 300}

library(scales)

max_value <- population  %>% 
  filter(property == property_name) %>%
  pull(estimate) %>%
  max()

population %>% 
  filter(property == property_name) %>%   
  mutate(travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev()
  ) %>% 

ggplot() +
  
  theme_evgo_hbar() +
  
  theme(
    legend.position = "none",
  ) +
  
  scale_fill_viridis(option = colorscheme,
                   begin = 0.2,
                   end = 0.95,
                   direction = -1,
                   discrete = TRUE,
                   name = "travel time") +
  
  geom_col(aes(x = travel_time, y = estimate, fill = travel_time), 
           position = "identity",
           width = 0.8) +
  
  geom_text(aes(x = travel_time, y = estimate, label = comma(estimate)), 
           position = "identity",
           hjust = -0.1) +
  
  scale_y_continuous(name = "",
                     labels = comma,
                     expand = expand_scale(mult = c(0, 0)),
                     limits = c(0, max_value * 1.15),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)) +
  
  xlab("") +
  
  coord_flip()

```
\
**Racial/ethnic makeup of service area**  
```{r echo=FALSE, fig.height=4, fig.width=5.5, dpi=300}

max_value <- race_ethnicity  %>% 
  filter(property == property_name) %>%
  pull(percent) %>%
  max()

race_ethnicity %>% 
  filter(property == property_name) %>%
  arrange(desc(contour)) %>% 
  mutate(
         travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev()
  ) %>% 
  
  #plot
  ggplot(aes(x = re_group, y = percent,fill = travel_time)) +
  
    geom_col(position = position_dodge(width = .8),
           width = 0.7) +
  
    geom_text(aes(label = percent(percent)),
           position = position_dodge(width = .8),
           hjust = -0.1,
           vjust = .4) +
  
  xlab("") +
  scale_y_continuous(name = "",
                     labels = percent,
                     expand = expand_scale(mult = c(0, .01)),
                     limits = c(0, max_value * 1.15)) +
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  theme_evgo_hbar() +

  coord_flip() +  
  guides(fill = guide_legend(reverse = TRUE))


```
\
**Household income brackets**  
*by number of households*  
```{r echo=FALSE, fig.height=3.5, fig.width=5.5, dpi=300}

max_value <- hh_income  %>% 
  filter(property == property_name,
         income_group != "total") %>%
  pull(estimate) %>%
  max()

hh_income %>% 
  filter(property == property_name & income_group != "total" ) %>%
  arrange(desc(contour)) %>% 
  mutate(var_name_order = str_extract(income_group, "(?<=\\n\\$)\\d+") %>% as.numeric(),
         var_name = fct_reorder(income_group, var_name_order),
         travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev()
  ) %>% 
  
  #plot
  ggplot(aes(x = var_name, y = estimate, fill = travel_time)) +
  
  geom_col(position = position_dodge(width = .8),
           width = 0.7) +
  
  geom_text(aes(label = comma(estimate)),
           position = position_dodge(width = .8),
           hjust = -0.1,
           vjust = .4) +

  xlab("") +
  scale_y_continuous(name = "",
                     labels = comma,
                     expand = expand_scale(mult = c(0, 0)),
                     limits = c(0, max_value * 1.15),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)) + 
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  theme_evgo_hbar() +

  coord_flip() +  
  guides(fill = guide_legend(reverse = TRUE))

```
**Eductational attainment**  
*by residents over 25*  
```{r echo=FALSE, fig.height=3.5, fig.width=5.5, dpi=300}

max_value <- education  %>% 
  filter(property == property_name,
         education_group != "total") %>%
  pull(estimate) %>%
  max()

education %>% 
  filter(property == property_name & education_group != "total" ) %>%
  mutate(group_order = case_when(
                 education_group == "high school\nor less" ~ 1,
                 education_group == "associates or\nsome college" ~ 2,
                 education_group == "undergraduate\ndegre" ~ 3,
                 education_group == "postgrad or\nprofessional\ndegree" ~ 4
  )) %>% 
  
  arrange(desc(contour)) %>% 
  mutate(travel_time = fct_reorder(paste(contour, "min"), contour) %>% fct_rev(),
         education_group = fct_reorder(education_group, group_order),
        
  ) %>% 
  
  
  #plot
  ggplot(aes(x = education_group, y = estimate, fill = travel_time)) +
  
  geom_col(position = position_dodge(width = .8),
           width = 0.7) +
  
  geom_text(aes(label = comma(estimate)),
           position = position_dodge(width = .8),
           hjust = -0.1,
           vjust = .4) +

  xlab("") +
  scale_y_continuous(name = "",
                     labels = comma,
                     expand = expand_scale(mult = c(0, .01)),
                     limits = c(0, max_value * 1.14),
                     breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1), round(max_value * 1.1, -nchar(max_value) + 1) / 5)
                     ) +
  
  scale_fill_viridis(option = colorscheme,
                     begin = 0.2,
                     end = 0.95,
                     direction = -1,
                     discrete = TRUE,
                     name = "travel time") +
  
  theme_evgo_hbar() +

  coord_flip() +  
  guides(fill = guide_legend(reverse = TRUE))

```

```{r include=FALSE}
background_map <- 
  st_as_sf(mud_com_map %>% filter(property == property_name),
           coords = c("X","Y"),
           crs = 4326)


boundingbox <- 
background_map %>%  st_bbox()


width <- (boundingbox$xmax - boundingbox$xmin) %>% unname()
length <-(boundingbox$ymax - boundingbox$ymin) %>% unname()

if (length > width) {
  width_add <-  (length - width)/2
  
  xlimits <- c(unname(boundingbox$xmin) - (width_add),
               unname(boundingbox$xmax) + (width_add))
  ylimits <- c(unname(boundingbox$ymin), unname(boundingbox$ymax))
  
  
  
} else {
  length_add <- (width - length)/2
  
  ylimits <- c(unname(boundingbox$ymin) - (length_add),
               unname(boundingbox$ymax) + (length_add))
  xlimits <- c(unname(boundingbox$xmin), unname(boundingbox$xmax))
  
}


```

**Commuteshed commute flows**  
*darker colors indicate more commutes*  

```{r echo=FALSE, fig.height=7, fig.width = 5.5, dpi = 300}

mud_commuter_number <- 
  mud_commuters %>% 
  filter(property.x == property_name) %>% 
  summarise(mud_commuters = sum(mud_commuters)) %>% 
  pull(mud_commuters) %>% 
  round(digits = 0)

#dummy dataset (kludge to make plotting work)
background_map %>%

ggplot() +
  
  theme_evgo_map() +
  
  # kludge
  geom_sf(alpha = 0) +
  
  annotation_map_tile(type = "cartolight", zoom = 10, progress = c("none")) +
  
  scale_color_viridis(option = colorscheme,
                      begin = 0.2,
                      end = 0.3,
                      direction = -1,
                      name = "MUD\ncommuters",
                      guide = FALSE
                      ) +
  
  scale_alpha_continuous(range = c(0.01, 1),
                         guide = FALSE) +
  
  geom_curve(data = mud_com_map %>% 
             arrange(mud_commuters) %>% 
             filter(property == property_name),
             
             aes(x = X, y = Y,
                 xend = lon, yend = lat, 
                 color = mud_commuters, alpha = mud_commuters),
             curvature = -0.15,
             size = 0.6,
             lineend = "round") +
  
  geom_curve(data = hpcp_list_geocode %>% 
                    filter(property == property_name) %>% 
                    mutate(st_lon = lon + 0.1,
                           st_lat = lat - 0.1),
             aes(x = st_lon, y = st_lat, xend = lon, yend = lat),
             color = "#383838",
             curvature = -0.2,
             arrow = arrow(length = unit(0.1, "cm"), type = "closed"),
             size = 0.8,
             lineend = "round",
             ) +

  annotate(geom = "text",
         x = hpcp_list_geocode %>% 
           filter(property == property_name) %>% 
           pull(lon) + 0.1,
         y = hpcp_list_geocode %>% 
           filter(property == property_name) %>% 
           pull(lat) - 0.1,
         label = maplabel,
         hjust = 0,
         color = "#383838",
         size = 5) +
         
  coord_sf(xlim = xlimits, ylim = ylimits) 



```
### Commutershed
In addition to serving nearby MuD residents, the HPCP may also serve MuD residents that commute to nearby workplaces. The commutershed is constructed using the U.S. Cenus' Longitudinal Origin Destination Employment Survey (LODES) data. Approximately 
**`r paste(comma(mud_commuter_number))`** MuD residents commute to workplaces within a 1/2 mile of the HPCP.


**Commuteshed Fast Charger Availability**  
*Number of MUD commuters by number of fast charging plugs within 1 mile*  
```{r echo=FALSE, fig.height=4.5, fig.width=5.5, dpi=300, warning=FALSE}

#median_value <- dcfc_stations_commute  %>% 
#    filter(property == property_name,
#         !is.na(charge_network)) %>% 
#  mutate(charge_weight = mud_commuters * chargers) %>% 
#  group_by(charge_network) %>% 
#  summarize(median_charger_availability = median(charge_weight))


## summary stats

dcfc_distribution <- dcfc_stations_commute %>% 
      filter(property == property_name,
         !is.na(charge_network)
         ) %>% 
      group_by(property, geoid) %>% 
      summarise(commuters = mean(commuters), chargers = sum(chargers)) %>% 
      ungroup() %>% 
      group_by(property, chargers) %>% 
      summarise(mud_commute_totals = sum(commuters))

dcfc_distro_notesla <- dcfc_stations_commute %>% 
         filter(property == property_name,
         !is.na(charge_network),
         charge_network != "Tesla"
         ) %>% 
      group_by(property, geoid) %>% 
      summarise(commuters = mean(commuters), chargers = sum(chargers)) %>% 
      ungroup() %>% 
      group_by(property, chargers) %>% 
      summarise(mud_commute_totals = sum(commuters))


median_charging <- weighted.median(dcfc_distribution$chargers,
                                   dcfc_distribution$mud_commute_totals)
no_fast_charging <- round(dcfc_distribution %>% 
                          filter(chargers == 0) %>% 
                          pull(mud_commute_totals), 0)

median_charging_notesla <- weighted.median(dcfc_distro_notesla$chargers,
                                           dcfc_distro_notesla$mud_commute_totals)

no_fast_charging_notesla <- round(dcfc_distro_notesla %>%
                                  filter(chargers == 0) %>%
                                  pull(mud_commute_totals), 0)




max_value <- dcfc_stations_commute  %>% 
  filter(property == property_name) %>%
  pull(chargers) %>%
  max()

dcfc_stations_commute %>% 
  filter(property == property_name,
         !is.na(charge_network)) %>%
  group_by(charge_network) %>% 
  mutate(resident_fraction = commuters/sum(commuters)) %>% 
  ungroup() %>% 
  
ggplot() +
  
  geom_point(aes(x = factor(charge_network, levels = c("Other", "Tesla", "EVgo")), y = chargers), shape = 1) +
  geom_violin(aes(x = charge_network, y = chargers, weight = resident_fraction, fill = charge_network), draw_quantiles = c(0.25, 0.5, 0.75)) +
  
theme_evgo_hbar() +
  
scale_fill_viridis(option = colorscheme,
                   begin = 0.2,
                   end = 0.95,
                   direction = -1,
                   discrete = TRUE) +
  
 xlab("") +
 scale_y_continuous(name = "",
                   labels = comma,
                   expand = expand_scale(mult = c(0, .01)),
                   limits = c(0, max_value * 1.14),
                   breaks = seq(0, round(max_value * 1.1, -nchar(max_value) + 1),
                                round(max_value * 1.1,
                                      -nchar(max_value) + 1) / (round(max_value * 1.1,
                                                                    -nchar(max_value) + 1)/10))
                   ) +

coord_flip()


```
\


**Commuteshed L2 Charger Availability**  
*Number of MUD commuters by number of L2 charging plugs within 1/2 mile*  
```{r echo=FALSE, fig.width = 5.5, fig.dpi=300}

outlier_figure <- l2_join %>% 
  filter(property.x == property_name,
         l2_chargers > 100) %>%
  pull(mud_commuters) %>% 
  sum() %>% 
  round(0)
  

l2_join %>% 
  filter(property.x == property_name,
         l2_chargers <= 100) %>%
  
  
ggplot() +
    geom_histogram(aes(x = l2_chargers, weight = mud_commuters, fill = property.x),
                 binwidth = 1,
                 )+
  
  scale_fill_viridis(option = colorscheme,
                   begin = 0.2,
                   end = 0.2,
                   direction = -1,
                   discrete = TRUE,
                   guide = FALSE) +
  
 scale_y_continuous(name = "MuD commuter frequency", label = comma, expand = expand_scale(mult = c(0, .1))) +
 scale_x_continuous(name = "L2 Chargers", expand = expand_scale(mult = c(0, 0.005)), breaks = seq(0,100,10))+

 theme_evgo_hist()
  
  



l2_join %>% 
  filter(property.x == property_name) %>%
  mutate(l2_chargers_trunc = ifelse(l2_chargers > 101, 101, l2_chargers),
         outliers = ifelse(l2_chargers_trunc == 101, 101, NA)) %>% 
  group_by(outliers) %>% 
  mutate(outlier_binquant = sum(mud_commuters)) %>% 
  ungroup() %>% 
  mutate(outlier_binquant = min(outlier_binquant)) %>% 

ggplot() + 
    geom_histogram(aes(x = l2_chargers_trunc, weight = mud_commuters, fill = mud_commuters),
                 binwidth = 3,
                 color = "#909fad") +
  
    geom_histogram(aes(x = outliers, weight = mud_commuters),
                 na.rm = TRUE,   
                 binwidth = 3,
                 fill = "#b2ced1",
                 color = "#a7c4c7") +
  
    geom_curve(aes(x = 90, y =  (outlier_binquant/2) + (outlier_binquant/4), xend = 99.5, yend = outlier_binquant/2),
               color = "#383838",
               curvature = 0.4,
               arrow = arrow(length = unit(0.1, "cm"), type = "closed"),
               size = 0.8,
               lineend = "round") +
    

 

geom_text(aes(x = 90,
              y = (outlier_binquant/2),
              label = paste0("outliers\n100+ chargers\n(max = ", max(l2_chargers), ")")),
         hjust = .5,
         vjust = -1.2,
         color = "#383838",
         size = 4) +

scale_fill_viridis(option = colorscheme,
                   begin = 0.2,
                   end = 0.95,
                   direction = -1,
                   discrete = TRUE) +  
  
scale_y_continuous(name = "MuD commuter frequency", label = comma, expand = expand_scale(mult = c(0, .1))) +
scale_x_continuous(name = "L2 Chargers (binsize = 3) ", expand = expand_scale(mult = c(0, 0.005)), breaks = seq(0,100,5))
```

